---
title: "Orb_EX_AB_sym_analysis"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(devtools)   # install.packages("devtools")
library(steponeR) # install_github("jrcunning/steponeR")
library(tidyverse) # (install.packages("tidyverse")
```


#Importing Raw qPCR Data from Quant Studio Design and Analysis Software 
```{r}
# List Exuma symbiodinium data files
plates_EX <- list.files(path = "Data/qPCR_EX", pattern = ".txt", full.names = TRUE)

# Read in data and calculate target ratios
df_EX <- steponeR(files = plates_EX,
               delim = "\t", 
               target.ratios = "A.A", 
               fluor.norm = list(C = 2.234, D = 1, A = 1, B = 1),
               copy.number = list(C = 20, D = 3, A = 1, B = 1),
               ploidy = list(C = 1, D = 1, A = 1, B = 1),
               extract = list(C = 0.813, D = 0.813, A = 0.813, B = 0.813))
qpcr_EX <- df_EX$result

```

#Filtering out other species from EX Raw qPCR data
```{r}
# Import Sample Data 
library(readr)

raw_sample_data <- readxl::read_xlsx("Data/Sample_data/Ex_Sample_Data.xlsx")

#renaming  colomns of sample data to match qpcr data
sample_data_EX <- raw_sample_data %>%
  select(Sample.Name = sample_id, site, genus, species, depth = colony_depth_m, range)

# Joining sample data with qpcr data and removing NA samples
EX_Ofav <- right_join(sample_data_EX, qpcr_EX, by = "Sample.Name", all = TRUE) %>%
  filter(genus == "orbicella")

qpcr_EX_Ofav <- EX_Ofav %>%
  select(Sample.Name, File.Name, depth, A.CT.mean, B.CT.mean, C.CT.mean, D.CT.mean, A.CT.sd, B.CT.sd, C.CT.sd,
         D.CT.sd, A.reps, B.reps, C.reps, D.reps, A.A)
```

```{r}
# List Sandy Cay symbiodinium data files
plates_AB <- list.files(path = "Data/qPCR_AB", pattern = ".txt", full.names = TRUE)

# Read in data and calculate target ratios
df_AB <- steponeR(files = plates_AB, 
               delim = "\t", 
               target.ratios = "A.A", 
               fluor.norm = list(C = 2.234, D = 1, Orb = 1, A = 1, B = 1),
               copy.number = list(C = 20, D = 3, Orb = 1, A = 1, B = 1),
               ploidy = list(C = 1, D = 1, Orb = 2, A = 1, B = 1),
               extract = list(C = 0.813, D = 0.813, Orb = 0.982, A = 0.813, B = 0.813))
qpcr_AB <- df_AB$result %>%
  select(Sample.Name, File.Name, A.CT.mean, B.CT.mean, C.CT.mean, D.CT.mean, A.CT.sd, B.CT.sd, C.CT.sd,
         D.CT.sd, A.reps, B.reps, C.reps, D.reps, A.A)
```

#Import Depth Data and Add to qpcr_good df
```{r}
#library(readr)
sample_data_AB <- readxl::read_xlsx("Data/Sample_data/sample_data.xlsx") %>%
  select(Sample.Name = tube_label, depth = colony_depth_m)

qpcr_AB_Ofav <- right_join(sample_data_AB, qpcr_AB, by = "Sample.Name", all = TRUE)

```

```{r}
Ofav_qpcr <- rbind(qpcr_EX_Ofav, qpcr_AB_Ofav)
```

# Establishing Ratios
```{r}
# adjust CT for flouresence 
qpcr_flor <-Ofav_qpcr %>%
  mutate(A.CT.mean = A.CT.mean - 1, 
         B.CT.mean = B.CT.mean - 1,
         C.CT.mean = C.CT.mean - 1,
         D.CT.mean = D.CT.mean - 1)

# adjust CT to form ratio of Symbiont divided by Copy # (Currently a Placeholder #)
qpcr_copy_num <- qpcr_flor %>%
  mutate(N = 15) %>%
  mutate(A.N = 2^(N - A.CT.mean)/1,
         B.N = 2^(N - B.CT.mean)/1,
         C.N = 2^(N - C.CT.mean)/1,
         D.N = 2^(N - D.CT.mean)/1)

qpcr_prop <- qpcr_copy_num %>%
  mutate(A.N = ifelse(is.na(A.N), 0, A.N),
         B.N = ifelse(is.na(B.N), 0, B.N),
         C.N = ifelse(is.na(C.N), 0, C.N),
         D.N = ifelse(is.na(D.N), 0, D.N)) %>%
  rowwise() %>%
  mutate(total = sum(A.N + B.N + C.N + D.N))%>%
  mutate(A.prop = A.N/total, B.prop = B.N/total, C.prop = C.N/total, D.prop = D.N/total)


   
```


# Oranizing Raw qPCR Data
```{r}
# Convert NaN CT values to 0  
qpcr <- qpcr_prop %>%
 mutate(A.CT.mean = ifelse(is.na(A.CT.mean), 0, A.CT.mean),
         B.CT.mean = ifelse(is.na(B.CT.mean), 0, B.CT.mean),
         C.CT.mean = ifelse(is.na(C.CT.mean), 0, C.CT.mean),
         D.CT.mean = ifelse(is.na(D.CT.mean), 0, D.CT.mean))

# Samples that did not amplify for any symbionts
fails <- qpcr %>%
  filter(A.CT.mean == 0 & B.CT.mean == 0 & C.CT.mean == 0 & D.CT.mean == 0) 

# Samples that need to be rerun due to 1 technical replicate or SD > 1
reruns <- qpcr %>%
  filter(Sample.Name != "PTC", Sample.Name != "NTC") %>%
  filter(A.reps == 1 | B.reps == 1 | C.reps == 1 | D.reps == 1 | A.CT.sd > 1.05 | B.CT.sd > 1.05 | C.CT.sd > 1.05 | D.CT.sd > 1.05)

qpcr_data <- qpcr %>%
   filter(A.CT.mean != 0 | B.CT.mean != 0 | C.CT.mean != 0 | D.CT.mean != 0)

  
```

#Filtering out "bad" data/replicates
```{r}
#Determing which samples have 2 replicates in the data set 
dupes <- qpcr_data %>%
  group_by(Sample.Name) %>%
  count(vars = "Sample.Name") %>%
  filter(n > 1) 

#Gathering the full data for samples with 2 replicates
Ofav_dupes <- qpcr_data %>%
  filter(Sample.Name %in% dupes$Sample.Name) %>%
  arrange(Sample.Name)

#filtering out data with only 1 technical replicate
Ofav_dupes_f1 <- Ofav_dupes %>%
  group_by(Sample.Name) %>%
  filter(A.reps != 1, B.reps != 1, C.reps != 1, D.reps != 1) %>%
  ungroup()
  
# Average SD  
Ofav_dupes_f2 <- Ofav_dupes_f1 %>%
  rowwise() %>%
  mutate(avg_sd = mean(c(A.CT.sd, B.CT.sd, C.CT.sd, D.CT.sd), na.rm = TRUE)) %>%
  group_by(Sample.Name) %>%
  dplyr::filter(avg_sd == min(avg_sd)) 

# Raw Data with no replicates
qpcr_good <- qpcr_data %>%
  filter(!(Sample.Name %in% dupes$Sample.Name))


# Cleaned dataset from data that worked the first run and "clean" replicates 
Ofav_good <- qpcr_good %>%
  bind_rows(Ofav_dupes_f2)


need_2_clean <- Ofav_good %>%
  group_by(Sample.Name) %>%
  count(vars = "Sample.Name") %>%
  filter(n > 1) 

# Which Samples Were Duplicated and Still Need to be Rerun?
setdiff(Ofav_dupes$Sample.Name, Ofav_dupes_f2$Sample.Name)
# EX066, Ex0249 won't produce 2 technical replicates for symbionts
# EX0188 failed and do not have rerun data 

setdiff(fails$Sample.Name, Ofav_good$Sample.Name)

# Samples that need to be rerun
setdiff(reruns$Sample.Name, Ofav_dupes_f2$Sample.Name)
```


# Renaming symbiont columns to genus name and determing dominant symbiont of each sample 
```{r}
Ofav <- Ofav_good %>%
   mutate(Symbiodinium = case_when(A.prop > 0 ~ A.prop),
         Breviolum = case_when(B.prop > 0 ~ B.prop),
         Cladocopium = case_when(C.prop > 0 ~ C.prop),
         Durusdinium = case_when(D.prop > 0 ~ D.prop)) %>%
   mutate(Symbiodinium = ifelse(is.na(Symbiodinium), 0, Symbiodinium),
          Breviolum = ifelse(is.na(Breviolum), 0, Breviolum),
          Cladocopium = ifelse(is.na(Cladocopium), 0, Cladocopium),
          Durusdinium = ifelse(is.na(Durusdinium), 0, Durusdinium)) %>%
  mutate(dom_sym = case_when(B.prop > C.prop & B.prop > D.prop & B.prop > A.prop ~ "Breviolum",
                             C.prop > B.prop & C.prop > D.prop & C.prop > A.prop ~ "Cladocopium",
                             D.prop > B.prop & D.prop > C.prop & D.prop > A.prop ~ "Durusdinium",
                             A.prop > B.prop & A.prop > C.prop & A.prop > D.prop ~ "Symbiodinium")) %>%
  select(Sample.Name, depth, Symbiodinium, Breviolum, Cladocopium, Durusdinium, dom_sym) %>%
  ungroup()
  
```


# Stacked Bar Plot of Symbiont Composition per Sample in order of depth 
```{r}
a <- Ofav %>%
  select(Sample.Name, Symbiodinium, Breviolum, Cladocopium, Durusdinium) %>%
  gather(key = "sym", value = "value", -Sample.Name) 


ggplot(a, aes(x = Sample.Name, y = value, fill = sym)) +
  geom_bar(stat = "identity", position = "fill") +
  scale_fill_manual(values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c'))

```

#Dominant Symbiont Proportion across Depth
```{r}
dom_sym <- Ofav %>%
  select(Sample.Name, depth, dom_sym) %>%
  filter(depth != "NA") %>%
  mutate(depth_int = cut(depth, breaks = 8)) %>%
  group_by(depth_int, dom_sym) %>%
  summarise(ncol = n()) %>%
  mutate(n = sum(ncol), label = paste0("N =", n)) %>%
  mutate(prop = ncol/n)


ggplot(dom_sym, aes(x = as.factor(depth_int), y = ncol, fill = dom_sym)) +
  geom_bar(stat = "identity", position = "fill", size =20) +
  geom_text(aes(x = as.factor(depth_int), y = 1.05, label =label), inherit.aes = FALSE) +
  scale_fill_manual(values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c'))
```

# Dominant Symbiont Proportion less than 8m
```{r}
b <- Ofav %>%
  filter(depth < 8) %>%
  select(Sample.Name, depth, dom_sym) %>%
  filter(depth != "NA") %>%
  mutate(depth_int = cut(depth, breaks = 8)) %>%
  group_by(depth_int, dom_sym) %>%
  summarise(ncol = n()) %>%
  mutate(n = sum(ncol), label = paste0("N =", n)) %>%
  mutate(prop = ncol/n)

ggplot(b, aes(x = as.factor(depth_int), y = ncol, fill = dom_sym)) +
  geom_bar(stat = "identity", position = "fill", size =20) +
  geom_text(aes(x = as.factor(depth_int), y = 1.05, label =label), inherit.aes = FALSE) +
  scale_fill_manual(values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c'))
```


### Questions 
# 1. What is the probability of D-Dominance across depth
# 2. What is the probability of Symbiont Combinations
